Software Citation Principles

### 2016-07-25 sc-principles/software-citation-principles.tex
added text explaining decision on benchmarking use case

\katznote{I think we should merge this with B.1, as suggested in the google doc - the bullets are all the same}
\niemnote{the title and description are quite different---based on the description, this actually seems like 5} \katznote{somehow, the description is the same was copied from 5's - not sure why/how - but I don't think this matches the title at all.  The title matches 1.  It's a case of a researcher using someone else's software for a paper.  Unlike 1, which is general in terms of the use, likely a new science results, here the use of a benchmarking study, but again, the outcome is a paper that needs to cite the software.  I'm fairly confident we can delete this one entirely, as it is really subsumed within 1.  If we do this, we should do it in the google doc too.}

@@

>>>>

@@

After review of this use case, we decided that based on the title this falls under
use case 1, where a researcher uses someone else's software for a paper.
Unlike use case 1, which is general in terms of the use of software, here the
use leads to a benchmarking study---but the outcome in both cases is a paper
that needs to cite the software.
